---
title: "Board Exchange Stats, Models"
author: "Joshua G. Mausolf"
date: "1/23/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message=FALSE, warning=FALSE)
```



```{r cars, echo=FALSE}
source("analysis_source.R")

######################################
## Load Libraries & Data
######################################


library(Rmisc)
library(Hmisc)
library(tidyverse)
library(bbplot)
library(scales)
library(RColorBrewer)
library(ggthemes)


colors_neutral = rev(brewer.pal(n = 8, name = "Purples")[5:8])
colors_dem = rev(brewer.pal(n = 8, name = "Blues")[5:8])
colors_rep = c("#700009", "#99000D", "#D80012", "#EF3B2C")

colors_grey = rev(brewer.pal(n = 8, name = "Greys")[5:8])
#show_col(colors_grey)

colors_parties2 = c("#2129B0", "#969696", "#BF1200")
colors_parties1 = c(colors_dem[1], colors_neutral[1], colors_rep[1])
colors_parties0 = c("#2129B0", "#3A084A", "#BF1200")
#show_col(colors_parties0)

#Display a Pallete
#show_col(colors_dem)

#Overwrite bbplot finalise_plot() function
source("bb_finalise_plot_academic.R")
```




```{r}
df <- dfb %>%
  filter(lag_years == 1) 


#TODO
#recode sector with 4cats, if sector has <1 firm, eg. recode

#y, boardparty med, cluster party, 
m1 <- glm(new_bm_party_rep ~ 
                board_change_events_list +
                bp_pid2n_median, 
                #fec_cluster_party +
                #age_median +
                #female_yes_mean +
                #minority_yes_mean +
                #aa_hisp_yes_mean +
                #non_usa_yes_mean +              
            
                #outside_public_boards_median +
                #interlocking_yes_mean +

                #sector + 
                #industry +
                #lag_years + 
                #year,
              data = df, family = "binomial")



m2 <- glm(new_bm_party_rep ~ 
                board_change_events_list +
                bp_pid2n_median + 
                #fec_cluster_party +
                age_median +
                female_yes_mean +
                #minority_yes_mean +
                aa_hisp_yes_mean +
                #non_usa_yes_mean +              
            
                outside_public_boards_median,
                #interlocking_yes_mean +

                #sector + 
                #industry +
                #lag_years + 
                #year,
              data = df, family = "binomial")




m4 <- glm(new_bm_party_rep ~ 
                board_change_events_list +
                bp_pid2n_median + 
                fec_cluster_party +
                age_median +
                female_yes_mean +
                minority_yes_mean +
                aa_hisp_yes_mean +
                #non_usa_yes_mean +              
            
                outside_public_boards_median +
                #interlocking_yes_mean +

                sector + 
                #industry +
                #lag_years + 
                year,
              data = df, family = "binomial")


df <- dfb %>%
  filter(lag_years >= 1) 

m4 <- glm(new_bm_party_rep ~ 
                board_change_events_list +
                bp_pid2n_median + 
                fec_cluster_party +
                age_median +
                female_yes_mean +
                minority_yes_mean +
                aa_hisp_yes_mean +
                non_usa_yes_mean +              
            
                outside_public_boards_median +
                #interlocking_yes_mean +

                sector + 
                #industry +
                lag_years + 
                year,
              data = df, family = "binomial")


models <- list(m1, m2, m3, m4)

```


```{r}
stargazer2(models,
           odd.ratio = T,
           type = "text",
           star.cutoffs = c(0.05, 0.01, 0.001))
```


```{r}
stargazer2(m1,
           odd.ratio = T,
          covariate.labels = c("Board Member Event: Swap", "Republican Board", "Amphibious Firm",
                               "Republican Firm", "Median Age", "Median No. Outside Boards"),
           type = "text",
           star.cutoffs = c(0.05, 0.01, 0.001))
```


#Models

Could do logit models for new_bm, drop_bm s.t. party added or dropped is modeled
Could do a multinomial logit with a new variable where outcomes combine event, new/drop,


#Would be good to also do longitudinal models



e.g. 
action drop add
swap dem dem
swap dem rep
swap rep dem
swap rep rep

add rep
drop rep
add dem
drop dem

Could also model logit for whether there is an event match / partisan match for adds, swaps


Variables could include
board party
cluster party
board_mean party
board median party

fec_median_pid2
fec_median_ps

dime_cfscore_mean


board size
max board size
mean board size

lag years
year

equal swap

private firm



sector
industry

#might be able to get dummies for
women on board
minority on board

%women
%minority races




